### 2024-06-06 Scripts/Scripts-collection.Rmd
Update Scripts-collection.Rmd

```{r Fig S3h}
### code was provided in Fig 2i,j
```

@@

df_mge_abundance = read.csv(r"(\mobile_elements_finder-stats_comparisons-mge_abundance.csv)")
df_mge_abundance$species <- factor(df_mge_abundance$species,levels = c('EHMOS','corynebacterium','stenotrophomonas','pseudomonas','acinetobacter','klebsiella'))
my_comparisons <- list(c('EHMOS','corynebacterium'),c('EHMOS','stenotrophomonas'),c('EHMOS','pseudomonas'),
                       c('EHMOS','acinetobacter'),c('EHMOS','klebsiella'))

@@

# Sample dataset
nodes <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-draft_genomes-arg_sankey-nodes.csv)',header = F)
names(nodes) <- c('name')
links <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-draft_genomes-arg_sankey-links-scaled.csv)')

@@

df_plasmids_ani <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\plasmids_selected-ANI-NZ_CP010782.1_fraglen.csv)")

#replace patient name with patientID
df_plasmids_ani$query <- str_replace(df_plasmids_ani$query,'zhujianfen-zheyi','Patient_6')
colnames(df_plasmids_ani) <-  str_replace(colnames(df_plasmids_ani),'zhujianfen.zheyi','Patient_6')
#remove suffix: '.fasta' 
colnames(df_plasmids_ani) <- str_remove(colnames(df_plasmids_ani),'.fasta')
row.names(df_plasmids_ani) <- str_remove(df_plasmids_ani$query,'.fasta')

@@

bbone <- read_mauve_backbone(r'(E:\learning materials\graduate student\Lab-Data\Task-01-New\Processed-Data\MGEs\PLSDB\mauve_alignment\plasmids_publish_selected.backbone)',
                             ref=1, filter_low=0)
names <- c('NZ_CP010782.1',
           'Patient_6')
names(bbone$dna_segs) <- names

>>>>

```{r Fig S3h}
### code was provided in Fig 2i,j
```
### Figure 4
### --------------------------------------------------------------------------------------------------------------------------------------------

@@

df_mge_abundance = read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-stats_comparisons-mge_abundance.csv)")
df_mge_abundance$species <- factor(df_mge_abundance$species,levels = c('EHMOS','corynebacterium','stenotrophomonas','pseudomonas','acinetobacter','klebsiella'))
my_comparisons <- list(c('EHMOS','corynebacterium'),c('EHMOS','stenotrophomonas'),c('EHMOS','pseudomonas'),
                       c('EHMOS','acinetobacter'),c('EHMOS','klebsiella'))

@@

# Sample dataset
nodes <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-draft_genomes-arg_sankey-nodes.csv)',header = F) # save in the same file 'mobile_elements_finder-draft_genomes-arg_sankey.txt'
names(nodes) <- c('name')
links <- read.csv(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\mobile_elements_finder-draft_genomes-arg_sankey-links-scaled.csv)') # save in the same file 'mobile_elements_finder-draft_genomes-arg_sankey.txt'

@@

df_plasmids_ani <- read.csv(r"(LRT_microbiomes_critical_illness\Data_repository\Main_figures\plasmids_selected-ANI-NZ_CP010782.1_fraglen.csv)")
#remove suffix: '.fasta' 
colnames(df_plasmids_ani) <- str_remove(colnames(df_plasmids_ani),'.fasta')
row.names(df_plasmids_ani) <- str_remove(df_plasmids_ani$query,'.fasta')

@@

bbone <- read_mauve_backbone(r'(LRT_microbiomes_critical_illness\Data_repository\Main_figures\plasmids_selected.backbone)',
                             ref=1, filter_low=0)
names <- c('NZ_CP010782.1',
           'Patient_6')
names(bbone$dna_segs) <- names
